Git Learning Notes

### 2014-03-11 ch-moox/moox.tex
fix subsubsection numbering issus
moox structure adjusted

Molybdenum oxides \ce{MoO3} crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase exhibits anisotropic structure with strong bonding along [001] and [100] direction while Van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, for instance, field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion\cite{Sian2005}. This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photoabsorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerenes\cite{Li2003c}, and few layer \ce{MoS2}.\cite{Lin2012}  It will also be an important member of the Van der Waals heterostructures.\cite{Geim2013}

It may be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis. The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane. Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer. When the two more distant oxygen are included for one molybdenum atom, the coordination can be regards a sixfold, i.e,, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.\cite{Itoh2001a}

on \ce{MoO3} reviews.\cite{He2003}

\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method  and demonstrated the photodegradation of MB under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied. h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH.} were possible structure directing and stable agents. The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0eV$.

Hexagonal phase \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$).

\section{Syntheses Methods}
\subsection{literature review}
crystal-chemical principles. Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of Mo-O or W-O ensembles in comparison to cations of other elements. And no mixing of vibrations of the cationic sublattices with that of \ce{Mo-O} or \ce{W-O} lattices. So the structural features of \ce{Mo-O} or \ce{W-O} polyhedra are dominating factors affecting the vibration frequencies and thermodynamic values of the molybdates and tungstates.\cite{Fomichev1992}

@@

Assignment for \ce{A2MO4} is well grounded. Alkali metal cations with octahedral coordination occur below 230 $cm^{-1}$. For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.

\subsection{this work}

@@

\textbf{Synthesis.} In a typical synthesis, molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr. Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet. With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr. The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 minutes and lasted for 15 to 120 minutes. Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature. The receiving substrate was placed in downstream location where the temperature was about 400 to 670 \si{\degreeCelsius} according to open air temperature profile. To observe the formation of droplets, clean silicon substrate was coated with 9 nm molybdenum film using a magnetron sputter(Desk IV TSC, Denton Vacuum), followed by \ce{NaOH} dipping as described before. Then the substrate was placed into chamber for growth, where all the parameters remained unchanged except the absence of Mo powder source.

@@

\section{Discussion}

In vapor synthesis process, two growth mechanism exists: VS and VLS. VS process is widely accepted for the growth of \ce{MoO3}. Yet we caution that synthesis conditions should be scrutinized to determine the exact mechanism. \citeauthor{Li2002c} suggested a VS mechanism at 700 \si{\degreeCelsius} and VLS at 750 \si{\degreeCelsius} and higher.\cite{Li2002c} \citeauthor{Fibers2007} proposed a modified VS mechanism probably because the deposition occurs on \ce{Al2SiO5} with possible \ce{Al_{0.95}SiNa_{0.06}O_x} involved. Therefore temperature and possible impurity could potentially alter the growth mechanism. We divide the growth results into two categories: on Si substrate and on non-Si substrate to describe them respectively.

@@

Mo began to be oxidized into \ce{MoO3} at 500 \si{\degreeCelsius}, \ce{MoO3} vapor pressure began to increase rapidly above 700 \si{\degreeCelsius}. \cite{Margrave1967} And the MP of \ce{MoO3} is reported as 795 \si{\degreeCelsius}. With these facts in mind, we design the experimental parameters as listed in Table.~\ref{tab:mooxsi}. We should point out that these parameters are selected and optimized from a wide range of combinations. And when we discuss the influence of one parameter with different values, one should assume other parameters still adapt those listed in Table.~\ref{tab:mooxsi}.

@@

This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental\cite{Zeng1998,Li2002b} and theoretical\cite{Firment1983,Cora1997} studies. We also observed different shapes, i.e., elongated hexagonal using similar growth conditions. This is not an indication of different growth mode. It is a normal thermodynamic fluctuation. In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along a and c axis could develop some other ratio. And the coexistence of different planes in one growth suggests the similarity of free surface energies.

@@

As shown in Fig.~\ref{fig:mooxch}, the crystal structures and phase of as-synthesized samples were examined by XRD and Raman. The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628\AA, \emph{b}=13.855\AA, \emph{c}=3.6964\AA). The space group is $D_{2h}^{16}(Pbnm)$. This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}. In contrast, we shall see a different scenario in Section.~\ref{sec:nasi}, where the orientation is changed. The Raman spectrum of as-synthesized specimens also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data. As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved. The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}. The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes. The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively.    667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral. The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral. The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table.~\ref{tab:moram}.

\begin{table}[htb]
\centering
\caption{Experimental Raman peaks (\si{cm^{-1}}) assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
\begin{tabular}{llcll}
\toprule
this work & Sym.       &          & Assignment &   \\
\midrule
117      & $B_{2g}$    &           & $T_c$  & RCM  \\
129      & $B_{3g}$    &           & $T_c$  & RCM  \\
158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
218      & $A_g$       &           & $R_c$     & RCM  \\
247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
\bottomrule
\end{tabular}
\end{table}

The growth rates along different crystalline direction of \ce{MoO3} are presumably determined by the free surface energy. In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.

\subsection{FL}

FL materials attracts intensive research efforts recently. We first use liquid exfoliation method to prepare FL \ce{MoO3}. We then characterized the absorption feature and crystalline structures of the exfoliated \ce{MoO3} using UV-Vis and TEM. Then we calculate the optical contrast of FL \ce{MoO3} on \ce{SiO2}-Si, which serves as a guideline to identify FL \ce{MoO3} using optical microscope.

@@

After least-squares fitting, the coefficients $a$ and $n$ can be used to estimated the scattering in other wavelengths. The fitting of $n$ usually falls between -2 and -4. We examined the t40h line in Fig.~\ref{fig:moabs} and found the scattering part is almost zero. Therefore we did not perform aforementioned fitting. This is not always the case. In chapter on the \ce{WS2} section, we do need to do so.

@@

According to the corrected absorbance spectrum, optical band gap can be deduced, which is known as Tauc Plot.\cite{Tauc1972} The procedure is recapitulated here.

\begin{equation}\label{eq:tauc}
 (h\nu \alpha)^{\frac{1}{n}} = B(h\nu - E_g^{opt}),
\end{equation}
where B is a proportional coefficient, $\alpha$ is absorption\footnote{The absorbance $A = 0.4343\alpha*l$, where l is the optical path} and $E_g^{opt}$ is defined as optical band gap. The value n is correlated to the nature of optical transition. For direct allowed transition, n = 1/2; For direct forbidden transition, n = 3/2; For indirect allowed transition, n = 2; And for indirect forbidden transition, n = 3. When the transition nature of sample is not well known, one should apply each to check which one provide the best fit. Depending on the synthesis methods and \ce{MoO3} morphologies, the transition phenomena might vary. On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} not.\cite{Szekeres2002} We use n = 2 in this work. We plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis. The intercept is used as $E_g^{opt}$ then. Our evaluation and some previous studies is summarized in Table.~\ref{tab:mobg}.

@@

An alternative way is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$. The band gap value can be obtained from the intercept of extrapolated line on photo energy axis.\cite{Choopun} This approach is not difficult to comprehend as long as we notice from Eq.~\ref{eq:tauc}, $Y = B (h\nu - E_g^{opt})^n$ and $Y' = B n(h\nu - E_g^{opt})^{n-1}$.

@@

Nevertheless, identifying these few layer \ce{MoO3} under optical microscope is still difficult due to both the small flake size and low contrast.\footnote{Human eye threshold contrast (contrast sensitivity)$^{-1}$ is about}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{Na2MoO4_Phase}
\caption[Phase diagram of Na-Mo-O]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from ref.~\cite{Hoermann1929}}
\label{fig:pd}
\end{figure}

@@

>>>>

Molybdenum oxides \ce{MoO3} crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3})exhibits anisotropic structure with strong bonding along [001] and [100] direction while Van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, for instance, field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion\cite{Sian2005}. This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photoabsorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerenes\cite{Li2003c}, and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the Van der Waals heterostructures.\cite{Geim2013}

In this thesis, we developed a new method to prepare \ce{MoO3} by using alkaline oxides as catalysts. This newly discovered a vapor-liquid-solid growth mechanism produced two new \ce{MoO3} structures: long nanoribbons and microscale towers. We then investigated the phase and crystalline structures of these new morphologies, and demonstrated the application in photocatalyst and electrochromic devices.

\section{Synthesis and Properties of Molybdenum Oxides}

\subsection{Growth of molybdenum oxides}

Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures. We will not try to exhaust these efforts since it has been well summarized in several review articles.\cite{He2003} So we only gave a brief introduction here. Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches. \citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}. Both methods have its own merits. Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; while vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time. Both methods are scalable for industrial applications. However the hydrothermal treatment seems to allow more  nanostructures control than do the vapor deposition method. Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one. The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures. \citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of MB under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied. h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents. The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0eV$. Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$).

In spite of these numerous growth of \ce{MoO3}, we point out that reports on VLS mechanism and other than Si substrates are still scarce. We will explore these relative new domains and present our results in Sec.~\ref{sec:result}.

\subsection{Crystal structures and chemical features of molybdenum oxides}

The coordination number of Mo in \ce{MoO3} is six, so usually \ce{MoO6} octahedra are considered as the building blocks. As shown in Fig, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.

While considering the fact that four of the six surrounding O atom are at distances from 1.67\AA to 1.95\AA, while the remaining two are as far as 2.25 and 2.33\AA, \ce{MoO3} could be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis. The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane. Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.\cite{Itoh2001a} This also stress that the \ce{MoO6} octahedra are rather distorted.

Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of Mo-O or W-O ensembles in comparison to cations of other elements. And no mixing of vibrations of the cationic sublattices with that of \ce{Mo-O} or \ce{W-O} lattices. So the structural features of \ce{Mo-O} or \ce{W-O} polyhedra are dominating factors affecting the vibration frequencies and thermodynamic values of the molybdates and tungstates.\cite{Fomichev1992}

@@

Raman band assignment for \ce{A2MO4} is well grounded. Alkali metal cations with octahedral coordination occur below 230 $cm^{-1}$. For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.

Molybdenum bronze also exhibits intriguing features, for instance, charge-density-wave states\footnote{In CDW states, conductivity is non-Ohmic above a threshold electric field} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} is side=centered monoclinic phase, with lattice parameter $a=18.249$\AA, $b=7.561$\AA, $c=9.856$\AA, and $\beta=117.54$ at RT. \ce{K0.3MoO3} presents a semiconductor-to-metal transition at 180 K. Electrical transport measurements yield an highly anisotropic ratio of DC conductivities of 1:10:1000. Along this high conducting axis, metallic reflection behavior is confirmed by optical measurements. Therefore, this blue bronze $\ce{K_{0.3}MoO3}$ is known as quasi-1D metal.\cite{Sing1999}

\subsection{Synthesis methods in this theis}

@@

\textbf{Synthesis.} In a typical synthesis (Fig.~\ref{fig:mooxgrowth}), molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr. Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet. With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr. The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 minutes and lasted for 15 to 120 minutes. Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature. The receiving substrate was placed in downstream location where the temperature was about 400 to 670 \si{\degreeCelsius} according to open air temperature profile. To observe the formation of droplets, clean silicon substrate was coated with 9 nm molybdenum film using a magnetron sputter(Desk IV TSC, Denton Vacuum), followed by \ce{NaOH} dipping as described before. Then the substrate was placed into chamber for growth, where all the parameters remained unchanged except the absence of Mo powder source.

@@

\section{Discussion on molybdenum oxides}\label{sec:result}

In vapor synthesis process, two growth mechanism exists: VS and VLS. VS process is widely accepted for the growth of \ce{MoO3}. Yet we caution that synthesis conditions should be scrutinized to determine the exact mechanism. \citeauthor{Li2002c} suggested a VS mechanism at 700 \si{\degreeCelsius} and VLS at 750 \si{\degreeCelsius} and higher.\cite{Li2002c} \citeauthor{Fibers2007} proposed a modified VS mechanism probably because the deposition occurs on \ce{Al2SiO5} with possible \ce{Al_{0.95}SiNa_{0.06}O_x} involved. Therefore temperature and possible impurity could potentially alter the growth mechanism. We divide the growth results into two categories: on Si substrate and on non-Si substrate, and describe them respectively. We also briefly mention using liquid exfoliation to prepare few layer \ce{MoO3}.

@@

Mo began to be oxidized into \ce{MoO3} at 500 \si{\degreeCelsius}, \ce{MoO3} vapor pressure began to increase rapidly above 700 \si{\degreeCelsius}. \cite{Margrave1967} And the melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}. With these facts in mind, we design the experimental parameters as listed in Table.~\ref{tab:mooxsi}. We should point out that these parameters are selected and optimized from a wide range of combinations. And when we discuss the influence of one parameter with different values, one should assume other parameters still adapt those listed in Table.~\ref{tab:mooxsi}.

@@

This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental reports\cite{Zeng1998,Li2002b} and theoretical studies.\cite{Firment1983,Cora1997} We also observed different shapes, i.e., elongated hexagonal using similar growth conditions. This is not an indication of different growth mode. It is a normal thermodynamic fluctuation. The growth rates along different crystalline direction of \ce{MoO3} are determined by the free surface energy. In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along $a$ and $c$ axis could develop some other ratio. And the coexistence of different planes in one growth suggests the similarity of free surface energies between these surfaces. In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.

@@

As shown in Fig.~\ref{fig:mooxch}, the crystal structures and phase of as-synthesized samples were examined by XRD and Raman. The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628\AA, \emph{b}=13.855\AA, \emph{c}=3.6964\AA). The space group is $D_{2h}^{16}(Pbnm)$. This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}. In contrast, we shall see a different scenario in Section.~\ref{sec:nasi}, where the orientation is changed.

\begin{table}[htb]
\centering
\caption{Experimental Raman peaks assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
\begin{tabular}{llcll}
\toprule
this work(\si{cm^{-1}}) & Sym.       &          & Assignment &   \\
\midrule
117      & $B_{2g}$    &           & $T_c$  & RCM  \\
129      & $B_{3g}$    &           & $T_c$  & RCM  \\
158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
218      & $A_g$       &           & $R_c$     & RCM  \\
247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
\bottomrule
\end{tabular}
\end{table}

The Raman spectrum of as-synthesized specimens also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data. As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved. The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}. The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes. The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively. 667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral. The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral. The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table.~\ref{tab:moram}.

\subsection{Liquid exfoliation on as-grown molybdenum oxides}

Few layer (FL) materials attracts intensive research efforts recently. We studied using liquid exfoliation method to prepare FL \ce{MoO3}. We then characterized the absorption feature and crystalline structures of the exfoliated \ce{MoO3} using UV-Vis and TEM. Then we calculate the optical contrast of FL \ce{MoO3} on \ce{SiO2}-Si, which serves as a guideline to identify FL \ce{MoO3} using optical microscope.

@@

After least-squares fitting, the coefficients $a$ and $n$ can be used to estimated the scattering in other wavelengths. The fitting of $n$ usually falls between -2 and -4. We examined the t40h line in Fig.~\ref{fig:moabs} and found the scattering part is almost zero. Therefore we did not perform aforementioned fitting. This is not always the case. In Chapter on the \ce{WS2} section, we do need to do so.

@@

According to the corrected absorbance spectrum, optical band gap can be deduced, which is known as Tauc Plot.\cite{Tauc1972} The procedure is recapitulated here. Eq.~\ref{eq:tauc} is given to empirically relate optical band gap to absorption.

\begin{equation}\label{eq:tauc}
 (h\nu \alpha)^{\frac{1}{n}} = B(h\nu - E_g^{opt}),
\end{equation}
where B is a proportional coefficient, $\alpha$ is absorption\footnote{The absorbance $A = 0.4343\alpha*l$, where l is the optical path} and $E_g^{opt}$ is defined as optical band gap. The value n is correlated to the nature of optical transition. 
\begin{itemize}
\item For direct allowed transition, n = 1/2;
\item For direct forbidden transition, n = 3/2;
\item For indirect allowed transition, n = 2; 
\item And for indirect forbidden transition, n = 3.
\end{itemize}

When the transition nature of sample is not well known, one should apply each to check which one provide the best fit. Depending on the synthesis methods and \ce{MoO3} morphologies, the transition phenomena might vary. On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} not.\cite{Szekeres2002} We use n = 2 in this work, plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis. The intercept is used as $E_g^{opt}$ then. Our evaluation and some previous studies is summarized in Table.~\ref{tab:mobg}.

@@

An alternative apporach is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$. The band gap value can be obtained from the intercept of extrapolated line on photo energy axis.\cite{Choopun} This approach is not difficult to comprehend as long as we notice from Eq.~\ref{eq:tauc}, $Y = B (h\nu - E_g^{opt})^n$ and $Y' = B n(h\nu - E_g^{opt})^{n-1}$. The advantage is one can also estimate n without using assumption.

@@

Nevertheless, identifying these few layer \ce{MoO3} under optical microscope is still difficult due to both the small flake size and low contrast.\footnote{Human eye threshold contrast (contrast sensitivity)$^{-1}$ is about 10\%.} One need to improve the liquid exfoliation process to obtain larger dimension and high yield. This is however beyond the scope of current study.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{Na2MoO4_Phase}
\caption[Phase diagram of Na-Mo-O system]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from ref.~\cite{Hoermann1929}}
\label{fig:pd}
\end{figure}

@@

\subsubsection{Phase evolution probing by Raman}

\citeauthor{Hardcastle1990} summarized an empirical formula to relate the Raman peaks and \ce{Mo-O} bonding lengths.\cite{Hardcastle1990} This correlation assumes general form as
\begin{equation}\label{eq:mobond}
\nu = A \exp{B\cdot R},
\end{equation}
where $A=32895$ and $B=-2.073$ are fitting parameters, R is bond distance in unit of \AA. Given a stretching frequency, the resolution for calculated bond distance is $\pm0.016$\AA. Another empirical expression connect the bond valence $s$ and bond distance R: $s(M-O) \approx (R/X)^{-6} $, where X=1.882 when M is Mo, and 1.904 when M is W. The valence sum rule could be then used to check the state of Mo cation. It should be noticed that not all observed Raman lines could be correlated to a \ce{Mo-O} bond distance by extrapolation of Eq.~\ref{eq:mobond}. It is then regarded as a symmetry related vibrational mode, i.e. $820 cm^{-1}$ in \ce{MoO3}. From the correlation of various Mo compounds, a general conclusion is the lower the stretching frequency for the shortest metal-oxygen bond, the more regular is the structure.

\textbf{Fundamental of VLS}

Vapor-Liquid-Solid (VLS) process is first proposed by Wagner,\cite{Wagner1964} and further developed by \citeauthor{Givargizov1975}.\cite{Givargizov1975} This method has become an important strategy for synthesizing one-dimensional nanostructures.\cite{Lieber1998} Conventionally, a liquid eutectic droplet is formed by catalyst itself or by alloying with the growth material, acting as a trap of growth species. The growth is initialized by supersaturation of the liquid alloy and subsequent precipitation at the solid-liquid interface. The choice of catalyst usually is among the several noble metals since they are physically active but chemically stable or inert in most growth scenarios. The growth materials span a wide range including group IV,\cite{Hochbaum2005} group III-V,\citep{Dalacu2013, Xiao2012, Dubrovskii2011} group II-VI,\cite{Hao2006} and some metal oxides, such as \ce{ZnO},\citep{Huang2001a,Ramgir2010} \ce{MgO},\citep{HEUER1967, Nagashima2007} \ce{SiO2},\cite{Pan2002} and \ce{TiO2},\cite{Zhuge2012} to name a few. The catalysts can be Au, Pd, Pt, Ni,\cite{Xiao2012} Ti, Ga,\cite{Pan2002} and even KI.

Understanding the interaction between liquid droplet and the solid interface allows for a rich engineering space to fine tune the geometry and structures of as-grown nanostructures. For instances, the diameter of Si nanowires (NWs) can be controlled by laser ablated catalyst\cite{Morales1998} or well-defined Au nanoparticles.\cite{Cui2001b} Under proper conditions,  axial modulation can produce nanowire superlattices from group IV and III-V materials.\citep{Gudiksen2002,Bjork2002}  Radial composition modulation have also been demonstrated by selectively suppressing VLS process, providing a robust routine for homogeneous or heterogeneous core-shell structures.\cite{Lauhon2002a}  \citeauthor{Wang2013c} changed the NW growth direction by changing the shape of droplets; \citeauthor{Biswas2013} reported enhanced aspect ratio of Ge NWs from bimetallic alloy.
